Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
editing safety spec
Diff between controller error and state space error

@@

The states must be computed considering 
the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
and disregarding it in the state equation~\eqref{eq:plant}. 
Thus, the states are computed using the following equations:
%
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}

>>>>

There are two sources of error due to numeric representation; the numeric error introduced by 
the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
the states as a fixed-point number. In this section we formally outline the errors introduced by
fixed point representation of numbers; in further sections we will differentiate between these
two errors by referring to them as the \emph{plant error} and the \emph{digital controller error}.

@@

The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and
digital controller, and the digital reference signal. In this paper, we consider systems with
a reference signal equal to zero. 
%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
%and disregarding it in the state equation~\eqref{eq:plant}.
Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$
to denote numbers represented with the precision of the digital controller. All other numbers
are represented with the precision of our plant model:
%
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})) \\
x_{k+1}&=Ax_{k}+Bu_{k}
\end{align*}
%\left\lbrace
%\begin{array}{l}
%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
%x_{k+1}=Ax_{k}+Bu_{k}
%\end{array}\right.
%\end{equation}
